Untitled

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
Redo with accontable, reusable and updatable themes

<!-- Add aims text here -->
We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people. <!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->In this paper, we describe:

- guidelines for quality implementation of OSHEMS;
- a framework for standardised and reproducible approaches to apply these guidelines to each component of the  **readyforwhatsnext** model; 
- a worked example of the first **readyforwhatsnext** model component developed using this framework.

>>>>

<!-- Add aims text here -->
In this paper, we introduce a framework for developing youth mental health OSHEMs. Specifically we describe:

- a set of guidelines for implementing OSHEMs;

- a toolkit for applying these guidelines in youth mental health; and

- a worked example of a modelling project developed with the toolkit.

<!-- We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health.  -->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
Redo with accontable, reusable and updatable themes

>>>>

## readyforwhatsnext
Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995]. Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.

Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts. Progress is reported on a project website [@rfwn2022].

## Utility mapping

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Guidelines.Rmd
Redo with accontable, reusable and updatable themes

Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems. <!-- such as Git [@git20XX].  --> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY**:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid.

## Transparent Models
A range of tools and practices are available to help make model code and data accessible, comprehensible and citable. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts. <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. -->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.

@@

Guidelines:

- **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories**
<!-- T2 MISSING - Merged With T1 -->

- **T2: Model code and data are documented **<!-- Was T3 -->

- **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->

- **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->

- **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->

- **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->

## Iterative Models
To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. <!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.  -->
<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

Guidelines:

- **I1: Model code and data are version controlled** <!-- Was I2 -->

- **I2: Model code and data use semantic versioning** <!-- Was I1 -->

- **I3: Continuous integration is used to verify model code updates**

- **I4: Deprecation conventions are used to retire model code and data**

## Modular Models
Modular health economic models link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013]. Many types of mental health data are highly sensitive with strict confidentiality requirements. For this reason, not all data included in some mental health models can be made widely available for others to re-use. A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components. An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].

Guidelines:

- **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->

- **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->

## Epitomising Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

@@

Guidelines:

- **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->

- **E2: Model code defines inheriting data-structures**

- **E3: Test data is available to demonstrate generalised applications of model code**

## Licensed Models
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

@@

Guidelines:

- **L1: Model code is made available for re-use under copyleft or permissive licenses**

- **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)**

- **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->

## Yielding Models
OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users. 
<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->

Guidelines:

- **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) -->
- **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->

>>>>

Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through digital repository services <!-- such as GitHub [@github2007] and Zenodo [@Zenodo2013] --> and the use of version control systems. <!-- such as Git [@git20XX].  --> Based on these and other existing sources of guidance and our own experience, we propose 20 guidelines for implementing OSHEMs that are **TIMELY** (Transparent, Iterative, Modular, Epitomising, Licensed and Yielding - see Table \@ref(tab:timelygls)).

 <!-- - **Transparent**: people can easily see how a model has been implemented and tested; -->
 <!-- - **Iterative**: a model is routinely updated to maintain and improve validity; -->
 <!-- - **Modular**: models and their components can be combined to extend their scope; -->
 <!-- - **Epitomising**: model code is sufficiently general to be be re-used in multiple decision contexts; -->
 <!-- - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and -->
 <!-- - **Yielding**: a model can be simply, flexibly and reliably used as a decision aid. -->

```{r, child = child_docs_ls$one, echo=FALSE}
```

## Transparent models
A range of tools and practices are available to help make models more transparent. The most efficient way to widely disseminate code and data may be to use existing open science infrastructure [@Erdemir2020] to make permanently accessible and uniquely identfied digital artefacts. <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each unique item. These repositories are a preferable solution for sharing citable code and data than transitory repositories such as corporate websites or GitHub where items can be deleted or relocated at any time [@sseditors2022]. Zenodo includes tools that automate integration with GitHub, which makes it easy for developers to maintain parallel code repositories - one for disseminating the most up to date development code and the other for archiving citable code releases. -->Model code and data also need to be clearly documented, potentially with different versions for technical and non-technical users [@Eddy2012]. <!-- Developers storing data in a Dataverse installation have access to multiple meta-data fields to document both a data collection and its individual constituent files.  --><!-- In R, code manuals and websites can be created with the aid of tools such as devtools [@devtools2021], sinew [@sinew2022], roxygen2 [@roxygen2021] and pkgdown [@pkgdown2022].  -->Consistent use of meaningful naming conventions when authoring code is recommended [@Wilson_2017; @Alarid2019]. Code can be made easier to follow by using the practices of abstraction [@8717448], where only simple, high level commands are routinely exposed to reviewers, and polymorphism [@7181447], where the same command (e.g. "simulate") can be reused to implement different algorithms of the same type. Programs to implement model analyses can be made comprehensible to even non-technical users through the use of literate programming techniques <!-- that use tools like RMarkdown [@xie2018r]  -->to render documents that integrate computer code with plain English descriptions.

@@

<!-- Guidelines: -->

<!-- - **T1: Uniquely identified copies of model code and data are permanently archived in open online repositories** -->
<!-- <!-- T2 MISSING - Merged With T1 -->

<!-- - **T2: Model code and data are documented **<!-- Was T3 -->

<!-- - **T3: Model code uses a simple and consistent syntax**<!-- Was T4 -->

<!-- - **T4: Model analyses and reporting are implemented using literate programming** <!-- Was T5 -->

<!-- - **T5: Code coverage is reported** <!-- New, replaces version now moved to T4 -->

<!-- - **T6: All parts of a study analysis and reporting workflow can be reproduced and/or replicated** <!-- Was T7, Replaces Deleted T6 -->

## Iterative models
To avoid OSHEMs going stale - losing validity and usefulness with time - they should be routinely updated.  Each update of code and data should be uniquely identifiable and retrievable, a goal that can be facilitated by use of version control tools [@Erdemir2020].<!-- A number of tools and approaches can make the process of implementing and curating changes to model code and data more coherent and efficient.   <!-- Repositories such as Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] provide persistent access to all published versions of a dataset, each uniquely identifiable. For code, use of version control tools like Git [@git20XX] can ensure that the entire development history of a project is organised so that each version is distinguishable and retrievable by developers. The online platform GitHub [@github2007] can make this version history accessible to anyone. -->Labeling each change using semantic versioning [@semver20xx] conventions can signal the potential importance of an update to users of model code and data. <!-- For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development (e.g. ExampleSoftware v1.1.1.1). Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention.  -->Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. <!-- OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub.  --><!-- These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).  -->
Finally, using deprecation conventions that take an informative and staged approach to retiring old code and data reduces the risk that model revisions have unintended consequences on third party users.  
<!-- The package lifeycle [@lifecycle2021] provides tools for R developers to consistently deprecate their code. -->

<!-- Guidelines: -->

<!-- - **I1: Model code and data are version controlled** <!-- Was I2 -->

<!-- - **I2: Model code and data use semantic versioning** <!-- Was I1 -->

<!-- - **I3: Continuous integration is used to verify model code updates** -->

<!-- - **I4: Deprecation conventions are used to retire model code and data** -->

## Modular models
An important consideration when combining model components (or modules) is to ensure that interactions between two modules do not compromise the validity of either. Using the coding practice of encapsulation [@8717448] can help ensure that model modules can be safely combined [@ready4oop2022].

<!-- Guidelines: -->

<!-- - **M1: Model code and data are stored and managed separately** <!-- Modified (lost ref to licensed and cited) -->

<!-- - **M2: Model code defines encapsulating data structures** <!--Replacement - Old version now merged with E1 -->

## Epitomising models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

@@

<!-- Guidelines: -->

<!-- - **E1: Model code is distributed as libraries of classes and functions**  <!-- Modified (lost ref to OOP and merged with M2) -->

<!-- - **E2: Model code defines inheriting data-structures** -->

<!-- - **E3: Test data is available to demonstrate generalised applications of model code** -->

## Licensed models
```{r echo = F}
gpl_pc_dbl <- get_license_share("GPL")
```

@@

<!-- Guidelines: -->

<!-- - **L1: Model code is made available for re-use under copyleft or permissive licenses** -->

<!-- - **L2: Non-confidential model data is licensed for liberal re-use (subject to additional terms for de-identified human data)** -->

<!-- - **L3: Model code and data are distributed with tools to support appropriate citation** <!-- New -->

## Yielding models
OSHEMs can be time and skills intensive for modellers to develop - but they should be easy for others to use. Statistical models are a common output of health economic evaluations, but they are often not reported in a format that enables others to confidently and reliably re-use them [@Kearns2013]. Open source approaches can help address this by disseminating code artefacts that enable easy and appropriate use of a statistical model to make predictions with new data. However, great care must be exercised when doing so if models are derived from data on human subjects as some software artefacts by default contain a copy of the source dataset. Such dataset copies must therefore be replaced (for example, with synthetic data) and the amended artefact's predictive performance then retested before any public release. Another way to make OSHEMs easier to use is to develop simple user-interfaces for non-technical users. 
<!-- In R, such user-interfaces are typically developed with the Shiny package, for which a tutorial aimed at health economists is available [@SmithR2020]. -->

<!-- Guidelines: -->

<!-- - **Y1: Statistical models are distributed with validated tools to support their safe and appropriate re-use** <!-- New, Replaces Old Y1 (now Y2) --> 
<!-- - **Y2: Simple user-interfaces allow non-technical users to configure and run models ** <!-- Was Y1 -->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
Redo with accontable, reusable and updatable themes

## readyforwhatsnext
Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995]. Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.

Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different jurisdictional decision contexts. Progress is reported on a project website [@rfwn2022].

## Framework toolkits
We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

### Framework repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022]. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].

### Framework software <!-- Novel ref -->

@@

```{r, child = child_docs_ls$one, echo=FALSE}
```

@@

>>>>

We have developed a toolkit to help streamline the process of developing OSHEMs that meet the TIMELY standards. The toolkit is comprised of online repositories and software.

## Repositories <!-- Existing ref -->
We created a GitHub organisation where all framework software source code is stored, documented, version controlled and continuously integrated [@ready4gh2022]. To store citable archived copies of release copies of our software, we created a Zenodo community [@ready4zen2022]. Finally, to manage datasets for use in models developed with the framework, we created a dedicated collection within the Harvard Dataverse  [@ready4dv2022].

## Software <!-- Novel ref -->

@@

@@

```{r, child = child_docs_ls$three, echo=FALSE}
```

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
Redo with accontable, reusable and updatable themes

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, these models routinely contain errors [@Radeva2020], are rarely adequately validated [@Ghabri2019] and can be difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017]. To help address these issues, there is support for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022].

Complex modelling projects may be more tractable when multiple modelling teams re-use, test and extend one another's work [@Arnold2010]. OSHEMSs might therefore mitigate some barriers to improving the longevity, quality and impact of health economic models.  For example,  health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Reference models that can be re-used in multiple health economic modelling projects have been advocated for [@Afzali2013] but require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022]. 
<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but complex models may be more prone to error [@Saltelli2019].  -->

@@

Despite the potential benefits of OSHEMs, actual implementations  are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations may also limit the uptake of OSHEMs [@Feenstra2022]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019].

<!-- Open source approaches have been recommended to help develop the mental health modelling field <!-- that rarely explores complex dynamic systems  -->
<!-- [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. -->

@@

>>>>

<!-- `r ifelse(is.na(params$X@background_1L_chr),"",params$X@background_1L_chr)`  -->
Computational models, particularly those addressing economic topics, have become essential tools for health policy development [@dakin2015influence; @Erdemir2020]. Although influential and widely used, health economic models typically have a number of limitations in accountability, reusability and updatability that at best restrict their usefulness and which in some cases may facilitate harmful misuse.

Accountability limitations of health economic models include inadequate validatation [@Ghabri2019], routinely containing errors [@Radeva2020] and, as with health policy computational models more generally, being difficult to reproduce [@Jalali2021; @McManus2019; @Bermejo2017]. Furthermore, models reflect the value judgments of their authors [potentially: https://doi.org/10.1177/0040571X221119276] relating to what questions to address, what features of a system to include, the weighting of different types of evidence and the type of stakeholders who are engaged in model design and validation [ESCAPE FROM MODEL LAND reference]. These values may at times be poorly aligned with those of the people whose lives are most impacted by decisions informed by model analyses [ESCAPE FROM MODEL LAND reference]. Some health economists have argued that more complex and sophisticated modelling methods are required to adequately explore some public health topics [@SQUIRES2016588].<!-- Systems modelling approaches have been recommended for public health economics topics [@SQUIRES2016588] but.  -->However, undertaking more ambitious models may accentuate accountability issues. More complex models may be more prone to propagation errors [@Saltelli2019]. The importance of accountability grows as models evolve from relatively simple implementations that address a single question to multipurpose tools [@Eddy2012; @Feenstra2022]. Transparency about the nature and extent of individual model authorship contributions can be harder to provide in models implemented over longer timeframes with a large team of collaborators [ESCAPE FROM MODEL LAND reference].

<!-- Modellers should be faithful to reaity and values of users DOI: 10.1002/asi.23697 -->

The resource and skills intensive task of model development can be made more tractable when modellers have the opportunity to re-use, test and refine the work of their peers [@Arnold2010]. However, as many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data[@Feenstra2022]. Many types of health data are highly sensitive with strict confidentiality requirements. For this reason, not all data included in some health economic models can be ethically made publicly available. Barriers to generalising and transferring health economic studies are often discussed in terms of study conclusions but also relate to model algorithms (can the same model logic be applied in different contexts?) and data (do shared taxonomies exist so that concepts have similar meanings in different jurisdictions?, which model parameters have values / sources that are context specific?) [Expand and add ref: https://link.springer.com/article/10.1186/s12962-021-00294-4, https://doi.org/10.1017/S026646232200321X].

Health economic models should be updated and refined as new evidence emerges and decision contexts change [@Jenkins2021], but this occurs infrequently [@Sampson2017]. Decision makers are frequently left to rely on economic analyses that become less valid and relevant each year. A model can grow stale when changes in the real world, whether sudden (e.g. new pandemics) or gradual (e.g. demographic), is not represented by corresponding updates to relevant model features. Even when the system being modelled remains relatively stable, new research findings may potentially invalidate aspects of a model's original conceptualisation and implementation. Funding for health economic modelling projects rarely extends to provision of medium term support for model updates and improvements. The career trajectories of health economists can also mitigate against adequate maintenance of a model, it being relatively common for model authors to have moved on from the team that owns the model IP and / or from working on the health condition for which the model was developed.

A potential strategy for improving model accountability, reusability and updatability is to make models modular and open-source.
<!-- Modularity -->
<!-- Definition, value - Computational biology https://doi.org/10.1371/journal.pcbi.1009513 -->
<!-- reusable, interoperable, trans- parent and able to accommodate updates to both data and algorithms - Ecology DOI: 10.1111/2041-210X.14034 -->
<!-- Brain OS modularity: https://www.frontiersin.org/articles/10.3389/fninf.2022.883223/pdf -->
A modular approach that ensures that model code and data are decoupled (stored in different files) can help model developers to restrict access to confidential model data, while providing open access to all other model components.
Modular approaches have been used in a small number of health economic models to link multiple self-contained components that can be independently reused and extended by other projects [@Trauer2017;@Urach2013]. Developing well validated reference models for re-used in multiple health economic modelling projects has been advocated for [@Afzali2013].
<!-- Standardized and transferable approaches to health economic modelling have been recommended. [doi:10.1017/S0266462317000666] -->

There appears to be in principle support from many health economists for greater use of open source health economic models (OSHEMs) that grant liberal permissions to access and re-use model source code and data [@Pouwels2022]. Despite the potential benefits of OSHEMs, actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of OSHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but guidelines for implementing OSHEMs remain scarce, piecemeal and need improving [@Sampson2019]. Open source is more than open access (limited discussion).

<!-- Reducing waste in research is responsibility of research funder: https://doi.org/10.1016/S0140-6736(13)62229-1 -->
<!-- MH Research priorities (WP3 - Research, WP6 - Economic) https://doi.org/10.1016/S2215-0366(15)00332-6 -->

@@

We plan to develop a modular OSHEM of youth mental health. Open source approaches have been recommended to help develop the mental health modelling field [@RN73] but only one mental health related model (in Alcohol Use Disorder [@Basu2018]) is currently indexed [RECHECK] in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. Other than our own work, we are aware of just one open source mental health reference model - in Major Depressive Disorder - that is currently in development [@IVIMDD2022]. 
<!-- that rarely explores complex dynamic systems  -->
<!-- [PECUNIA] -->

@@

<!-- CONTEXT: Funders should also support methodological work on context, including the development of reporting templates to facilitate accurate, comprehensive and systematic reporting of context, approaches to evidence synthesis that can capture contextual variation adequately and modelling methods that can leverage the accumulating evidence on contextual variation to predict the reach, implementation and effectiveness of promising interventions in new contexts." 
http://hdl.handle.net/1893/27205-->

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
Redo with accontable, reusable and updatable themes

# Guidelines
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```

# Framework
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```

>>>>

# Guidelines for OSHEMs
```{r child="../Child_RMDs/MS_Imp_Guidelines.Rmd", echo=FALSE}
```

# Modelling Toolkit
```{r child="../Child_RMDs/MS_Imp_Toolkit.Rmd", echo=FALSE}
```

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
table 1 rough draft done
circulated draft
Redo with accontable, reusable and updatable themes

```{r child="XX_Funs.Rmd", echo=FALSE}
```

```{r echo=FALSE}
if(params$X@tables_in_body_lgl){
  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
                      two = "../Child_RMDs/MS_Tables_2.RMD")
}else{
    child_docs_ls <- list(one = NULL,
                      two = NULL)
}
```

>>>>

```{r echo=FALSE}
if(params$X@tables_in_body_lgl){
  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.RMD",
                        two = "../Child_RMDs/MS_Tables_2.RMD",
                        three = "../Child_RMDs/MS_Tables_3.RMD")
}else{
    child_docs_ls <- list(one = NULL,
                      two = NULL)
}
```

### 2023-01-23 Markdown/Manuscript/Child_RMDs/MS_Tables_3.Rmd
Redo with accontable, reusable and updatable themes

                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures and was created to demonstrate generalised applications of study algorithms.",

@@

                                           "All libraries have CITATION file in inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data). The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applyihg models compatible with different types of input data. An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).  ",

>>>>

                                           "Two synthetic datasets and their data dictionaries are publicly available in a data repository [@DVN/HJXYKQ_2021]. One (ymh_clinical_tb.RDS) closely resembles the study dataset and was released so that the main study algorithm [@hamilton_matthew_2022_6129906] can be rerun by those without access to the confidential study dataset. The other (eq5d_ds_dict.RDS) is deliberately different to the source dataset in both variable naming convention and the concepts used for predictors and outcome measures. It was created to demonstrate generalised applications of study algorithms.",

@@

                                           "All libraries have a CITATION file in  the inst directory. All code repositories have a CITATION.cff file. All datasets have citation generating metadata.",
                                           "Model catalogues (PDF files beginning with 'AAA_TTU_MDL_CTG') are available in the study results dataset [@DVN/DKDIB0_2021] and describe the predictive performance of all models under a variety of usage regimes (including when the source dataset in the R model object is replaced with fake data). The youthu library [@matthew_p_hamilton_2021_5646669] includes tools for searching for and applying models compatible with different types of input data. An example program to demonstrate this functionality is available in both RMarkdown [@hamilton_matthew_2022_6416330] and rendered PDF formats (the 'Application.pdf' file in the study results dataset [@DVN/DKDIB0_2021]).  ",
